%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome5}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Adil Khwaja} \\ \vspace{0.3cm}
    \small  \href{tel:+919370131609}{\underline{\faPhone\ +91 9370131609}} $|$ \href{mailto:zadilkhwaja@gmail.com}{\underline{\faEnvelope\ zadilkhwaja@gmail.com}} $|$ 
    \href{https://linkedin.com/in/zadilkhwaja}{\underline{\faLinkedin\ linkedin.com/in/zadilkhwaja}} $|$
    \href{https://github.com/zadilkhwaja}{\underline{\faGithub\ github.com/zadilkhwaja}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  Experienced Full Stack Developer offering 2+ years of expertise. I enjoy the entire development process - from concept to delivery. Proven ability in improving user experience by 20\% and collaborating with cross-functional teams, integrating third-party services and APIs.

%-----------EXPERIENCE-----------
\section{Experience}
  
\resumeSubHeadingListStart
  \resumeSubheading
      {Nihilent Limited}{Pune, MH}
      {Software Engineer}{Jun. 2023 – Present}
      \resumeItemListStart
      \resumeItem{Working as a lead for Customer Facing Systems overlooking modules like checkout, payment, notifications and pricing. Owned Auth services, which included signup OTP, token validations.}
      \resumeItem{
      Engineered dynamic and responsive user interfaces,  resulting in a 25\% decrease in bounce rate.}
      \resumeItem{Built scalable back-end services \& Django REST API's. Implemented caching, server-side pagination and middleware's that reduced average response time by 50\%.}
      \resumeItem{Collaborated with the security team to implement data protection solutions, resulting in a 30\% reduction in security vulnerabilities.}
     \resumeItemListEnd
     
    \vspace{-\baselineskip}
    \resumeSubheading
      {}{}
      {Project Trainee}{Jun. 2022 – Jun. 2023}
      \resumeItemListStart
        \resumeItem{Developed robust database solutions, improving data retrieval times by 40\% and increase in system reliability.}
        \resumeItem{Implemented animated data visualizations, providing insights into user engagement and emotional responses.}
      \resumeItemListEnd

    \resumeSubheading
    {IIT Indore}{Remote}
      {Summer Research Intern}{Jul. 2021 – Oct. 2021}

  \resumeSubHeadingListEnd
  

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Database}{: Python, JavaScript, HTML5, CSS3, MySQL, MongoDB} \\
     \textbf{Libraries \& Frameworks}{: Django REST, React, jQuery, Flask} \\
     \textbf{Tools}{: Git, Docker, PowerBI, Postman} \\
    }}
 \end{itemize}
 

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RAG Based AI Chatbot} $|$ \emph{GenAI, Docker} $|$ \href{https://github.com/zadilkhwaja/RAG-Based-AI-Chatbot} {\underline{Link}}}{Sep. 2024}
          \resumeItemListStart
            \resumeItem{Enhanced data retrieval and generation capabilities with low-latency performance using LangChain and neo4j.}
            \resumeItem{Containerized using Docker Compose, simplifying the environment setup process by 70\%.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{TripSage AI Pro} $|$ \emph{React, Typescript, Tailwind} $|$ \href{https://github.com/zadilkhwaja/TripSageAIPro} {\underline{Link}}}{Aug. 2024}
          \resumeItemListStart
            \resumeItem{Utilized component-based architecture to build modular UI resulting in a 20\% reduction in development time.}
            \resumeItem{Used static type-checking to catch errors at compile-time and SquidAI on the backend.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{MIT Medicinal Plant Database} $|$ \emph{MongoDB, ExpressJS, NodeJS} $|$ \href{https://mitmpd.netlify.app/} {\underline{Link}}}{Sep. 2022}
          \resumeItemListStart
            \resumeItem{Designed an E-R diagram, data models \& aggregation pipelines improving database efficiency by 30\%.}
          \resumeItemListEnd
        
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MIT ADT University}{Pune, MH}
      {Integrated Master of Technology in Bioengineering - CGPA: 8.50/10.00}{Aug. 2018 – Jul. 2023}
      \resumeItemListStart
        \resumeItem{Relevant coursework: ML\&AI, OOPs, DSA, Big Data, Java \& Web Technology, Statistics, Data Analytics, IoT}
      \resumeItemListEnd
    \resumeSubheading
      {People’s Higher Secondary}{Panaji, GA}
      {HSSC Class XII - 84.2\%}{Mar. 2018}
      \resumeItemListStart
        \resumeItem{Awards: 1st Rank Science Stream and Student of the Year}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
    
%-----------AWARDS-----------
\section{Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Star for the Quarter - Nihilent Limited} }{Mar 2024}
    
      \resumeProjectHeading
        {\textbf{Innovative Solution Award - BETiC, IIT Bombay }(Medical Device Hackathon)} {May 2021}
        
        \resumeItemListStart
          \resumeItem{Prototyped interactive Human Anatomy VR experience with Haptic feedback mechanism.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
